The Evolution of Manufacturing Ecosystem in Cloud Manufacturing Architecture

### 2016-08-22 design.tex
resource schedule done

\subsubsection{Assumptions, nomenclature} % (fold)
\label{ssub:assumptions_nomenclature}
Assumptions about quality
about time

\begin{table}[!h]
\begin{tabularx}{\textwidth}{|lX|}
    \hline
    \multicolumn{2}{|l|}{\multirow{2}[0]{*}{\large\textbf{Nomencalture}}} \\
    \multicolumn{2}{|l|}{} \\
	$o_i$ & Order that come with demander \\
	$\mathcal{T}_i$ & Task set of $o_i$ \\
	$t_{ij}$ & Task belongs to $o_i$, $t_{ij}\in\mathcal{T}_i$ \\
	$p_{ij}$ & Process duration of $t_{ij}$\\
	$r_i$ & Release time of $o_i$\\
	$mr_k$ & Resource that come with provider \\
	$\delta_k$ & Quality of resource $mr_k$ \\
	$C_{k,\tau}$ & Capacity of $mr_k$ at time $\tau$\\
	$A_{k,\tau}$ & Available capacity of $mr_k$ at time $\tau$\\
	$\mathcal{L}_{k,\tau}$ & The set of job queue of $mr_k$ at $\tau$\\ 
	$\mathcal{A}$ & Resource type set \\
	$\mathcal{A}_{ij}$ & Resource type subset required by $t_{ij}$, $\mathcal{A}_{ij}\subset\mathcal{A}$\\
	$q_{\alpha,ij}$ & Required amount of resource with type $\alpha$ by $t_{ij}$\\
	$sc_l$ & Service-call generated by provider\\
	$p_l$ & Process duration of $sc_l$\\
	$r_l$ & Release time of $sc_l$\\
	$\mathcal{A}_l$ & Resource type subset required and provided by $sc_l$ and $ms_l$ respectively, $\mathcal{A}_l\subset\mathcal{A}$\\
	$ms_l$ & Service that generated after the finish of $sc_l$\\
	$\Delta_l$ & Overall quality of servicev $ms_l$\\
	$\bm{mr}_l$ & Resource member set of $ms_l$\\
	$\bm{q}_l$ & Resource member's capacity contribution set of $ms_l$\\
	$\mathcal{L}_{l,\tau}$ & The set of job queue of $ms_l$ at $\tau$\\
	$\mathcal{R}_{ij,\tau}$ & Resource candidates set for $t_{ij}$ to select\\
	$\mathcal{B}_{ij,\tau}$ & Resource candidate types set for $t_{ij}$\\
	$\mathcal{S}_{ij,\tau}$ & Service candidates set for $t_{ij}$ to select\\
	$\mathcal{R}_{l,\tau}$ & Resource candidates set for $sc_l$ to select\\
	$\mathcal{B}_{l,\tau}$ & Resource candidate types set for $sc_l$\\
	$R(\cdot)$ & Rank inquire function about provider\\
	$F(\cdot)$ & Owner inquire function about resource or service\\
	$P(\cdot)$ & Type inquire function about resource\\
	$\bm{x}$ & Bold font of the variable($x$) means the temp set of a bunch of these variables\\
    \hline
\end{tabularx}
\end{table}

@@

\begin{asparaenum}
\item $\mathcal{B}_{ij,\tau}\subset\mathcal{A}_{ij}$, while $|\mathcal{S}_{ij,\tau}|>0$.
\suspend{asparaenum}
\begin{equation}
\max_{\forall l}\left\{ \Delta_{l}, R\left(F\left(ms_{l}\right)\right), \abs{\mathcal{L}_{l,\tau}}\right\}
\end{equation}
\begin{numcases}{\text{s.t.}}
 ms_l \in \mathcal{S}_{ij,\tau} & \\
\Delta_l \sim \mathcal{N} \left(\mu_l,\sigma_l^2\right) & \\
\mu_l = mean\left( \bm{mr}_l , \bm{q}_l \right) & \\
\sigma_l = std\left( \bm{mr}_l , \bm{q}_l \right) & 
\end{numcases}

@@

\begin{equation}
\max_{\forall \bm{k}}\left\{ \delta_{\bm{k}}, 
R\left( F\left( mr_{\bm{k}} \right) \right), \abs{\mathcal{L}_{\bm{k},\tau} }
\right\}
\end{equation}
\begin{numcases}{\text{s.t.}}
q_{\alpha,ij} \le C_{k_{\alpha},\tau} & \\
R_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{ij,\tau}, P(mr) = \alpha \right\} & \\
mr_{k_{\alpha}} \in \mathcal{R}_{\alpha,\tau} & \\
\mathcal{R}_{ij} = \bigcup_{\alpha\in\mathcal{A}_{ij}}\mathcal{R}_{\alpha,\tau} & \\
\bm{k} = \left[k_1,k_2,\dots,k_\alpha,\dots\right] & \\ 
\forall\alpha\in\mathcal{A}_{ij} &
\end{numcases}
For each required resource type $\alpha$

@@

\begin{equation}
\max_{m\in\{l^*,\bm{k}^*\}} \left\{ \Delta_m, 
Rank_m, \mathcal{L}_m \right\}
\end{equation}
\begin{numcases}{\text{s.t.}}
q_{\alpha,ij} \le C_{k_{\alpha},\tau} & \\
R_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{ij,\tau}, P(mr) = \alpha \right\} & \\
mr_{k_{\alpha}} \in \mathcal{R}_{\alpha,\tau} & \\
\mathcal{R}_{ij} = \bigcup_{\alpha\in\mathcal{A}_{ij}}\mathcal{R}_{\alpha,\tau} & \\
\bm{k} = \left[k_1,k_2,\dots,k_\alpha,\dots\right] & \\ 
\bm{k}^* = \arg\left(\max_{\forall \bm{k}}\left\{ \delta_{\bm{k}}, 
R\left( F\left( mr_{\bm{k}} \right) \right), \abs{\mathcal{L}_{\bm{k},\tau} }
\right\}\right) & \\
Rank_{\bm{k}^*} = \min_{k\in\bm{k}^*} \left\{ R\left( F\left( mr_k \right) \right) \right\} & \\
\mathcal{L}_{\bm{k}^*} = \max_{k\in\bm{k}^*}\left\{ \abs{\mathcal{L}_{k,\tau}} \right\} & \\
\Delta_{\bm{k}^*} \sim \mathcal{N} \left(\mu_{\bm{k}^*},\sigma_{\bm{k}^*}^2\right) & \\
\mu_{\bm{k}^*} = mean\left( \bm{mr}_{\bm{k}^*} , \bm{q}_{\bm{k}^*} \right) & \\
\sigma_{\bm{k}^*} = std\left( \bm{mr}_{\bm{k}^*} , \bm{q}_{\bm{k}^*} \right) & \\
\bm{mr}_{\bm{k}^*} = \bigcup_{k\in\bm{k}^*}mr_k  &\\
\bm{q}_{\bm{k}^*}  =\bigcup_{\alpha\in\mathcal{A}_{ij}}q_{\alpha,ij} & \\
ms_l \in \mathcal{S}_{ij,\tau} & \\
\Delta_l \sim \mathcal{N} \left(\mu_l,\sigma_l^2\right) & \\
\mu_l = mean\left( \bm{mr}_l , \bm{q}_l \right) & \\
\sigma_l = std\left( \bm{mr}_l , \bm{q}_l \right) & \\
l^* = \arg\left( \max_{\forall l}\left\{ \Delta_{l}, R\left(F\left(ms_{l}\right)\right), \abs{\mathcal{L}_{l,\tau}}\right\}  \right) & \\
Rank_{l^*} = R\left( F\left( ms_{l^*} \right) \right) & \\
\mathcal{L}_{l^*} = \abs{\mathcal{L}_{l^*,\tau}} & \\
\forall\alpha\in\mathcal{A}_{ij} & 
\end{numcases}

\subsubsection{Provider}
\label{subs:Provider}
Provider makes decision for job response with regard to its resources and service, the job here means task and service-call. As we mentioned in the master plan, provider publish service-call according to the frequent accomplished tasks. Without loss of generalization, we suppose at time $\tau$, demander will make these decisions:

@@

Capacity will not return back to $mr_k$ until the corresponding service $ms_l$ was repealed. Decision making of provider $p_b$ likes the one of demander's, but the final decision $\bm{mr}_l$ and $\bm{q}_l$ don't have to meet $\abs{\bm{mr}_l} = \abs{\mathcal{A}_{ij}}$, because different resource with the same type can gather together to bundle into one service, the only condition in need is that
\begin{numcases}{}
\sum_{k\in\mathcal{R}_{\alpha,\tau}} q_{\alpha,k} = q_{\alpha,l} & $\forall\alpha\in\mathcal{A}_l$\\
R_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{l,\tau}, P(mr) = \alpha \right\} & $\forall\alpha\in\mathcal{A}_l$
\end{numcases}
\resume{asparaenum}
\item Response for the task need $t_{ij}$($\tau\ge r_i$) with service $ms_l$
\end{asparaenum}
Service is a combination contract among the participated resources and it's made oriented to the certain task, so the only condition for $ms_l$ to response $t_{ij}$ is:
\begin{numcases}{}
q_{\alpha,ij} = q_{\alpha,l} & $\forall\alpha\in\mathcal{B}_l$\\
\mathcal{A}_{ij} = \mathcal{B}_l
\end{numcases}

@@

\subsection{Operation mode} % (fold)
\label{sub:operation_mode}
The chief concern about operation mode for provider is the outsource mode and schedule method

>>>>

\subsubsection{Assumptions, nomenclature} % (fold)
\label{ssub:assumptions_nomenclature}
Assumptions about quality

about time

schedule and outsource are event driven decision making

\begin{table}[!h]
\begin{tabularx}{\textwidth}{|lX|}
    \hline
    \multicolumn{2}{|l|}{\multirow{2}[0]{*}{\large\textbf{Nomencalture}}} \\
    \multicolumn{2}{|l|}{} \\
	$o_i$ & Order that come with demander \\
	$\mathcal{T}_i$ & Task set of $o_i$ \\
	$t_{ij}$ & Task belongs to $o_i$, $t_{ij}\in\mathcal{T}_i$ \\
	$p_{ij}$ & Process duration of $t_{ij}$\\
	$r_i$ & Release time of $o_i$\\
	$f_{ij}$ & Actual finish time of $t_{ij}$ \\
	$f_{i}$ & Finish time of $o_i$\\
	$\mathcal{P}_{ij}$ & The set of predecessor of $t_{ij}$\\
	$mr_k$ & Resource that come with provider \\
	$\delta_k$ & Quality of resource $mr_k$ \\
	$C_{k,\tau}$ & Capacity of $mr_k$ at time $\tau$\\
	$A_{k,\tau}$ & Available capacity of $mr_k$ at time $\tau$\\
	$\mathcal{L}_{k,\tau}$ & The list of job queue of $mr_k$ at $\tau$ with sequence\\
	$\mathcal{G}_{k,\tau}$ & The set of active job (being processed) of $mr_k$ at $\tau$ \\ 
	$f^{(s)}_j$ & Ideal finish time of $t_j$ in $\mathcal{L}^{(s)}_{k,\tau_0}$ for schedule . \\
	$re_j$ & Remaining process time of $t_j$ in $\mathcal{G}_{k,\tau_0}$ for schedule . \\
	$\mathcal{A}$ & Resource type set \\
	$\mathcal{A}_{ij}$ & Resource type subset required by $t_{ij}$, $\mathcal{A}_{ij}\subset\mathcal{A}$\\
	$q_{\alpha,ij}$ & Required amount of resource with type $\alpha$ by $t_{ij}$\\
	$sc_l$ & Service-call generated by provider\\
	$p_l$ & Process duration of $sc_l$\\
	$r_l$ & Release time of $sc_l$\\
	$\mathcal{P}_{l}$ & The set of predecessor of $sc_{l}$\\
	$\mathcal{A}_l$ & Resource type subset required and provided by $sc_l$ and $ms_l$ respectively, $\mathcal{A}_l\subset\mathcal{A}$\\
	$ms_l$ & Service that generated after the finish of $sc_l$\\
	$\Delta_l$ & Overall quality of servicev $ms_l$\\
	$\bm{mr}_l$ & Resource member set of $ms_l$\\
	$\bm{q}_l$ & Resource member's capacity contribution set of $ms_l$\\
	$\mathcal{L}_{l,\tau}$ & The list of job queue of $ms_l$ at $\tau$ with sequence\\
	$\mathcal{G}_{k,\tau}$ & The set of active job (being processed) of $ms_l$ at $\tau$ \\
	$\mathcal{R}_{ij,\tau}$ & Resource candidates set for $t_{ij}$ to select\\
	$\mathcal{B}_{ij,\tau}$ & Resource candidate types set for $t_{ij}$\\
	$\mathcal{S}_{ij,\tau}$ & Service candidates set for $t_{ij}$ to select\\
	$\mathcal{R}_{l,\tau}$ & Resource candidates set for $sc_l$ to select\\
	$\mathcal{B}_{l,\tau}$ & Resource candidate types set for $sc_l$\\
	$R(\cdot)$ & Rank inquire function about provider\\
	$F(\cdot)$ & Owner inquire function about resource or service\\
	$P(\cdot)$ & Type inquire function about resource\\
	$\bm{x}$ & Bold font of the variable($x$) means the temp set of a bunch of these variables\\
    \hline
\end{tabularx}
\end{table}

@@

\begin{asparaenum}
\item $\mathcal{B}_{ij,\tau}\subset\mathcal{A}_{ij}$, while $|\mathcal{S}_{ij,\tau}|>0$.
\suspend{asparaenum}
\begin{equation}
\max_{\forall l}\left( \Delta_{l}, R\left(F\left(ms_{l}\right)\right), \abs{\mathcal{L}_{l,\tau}}\right)
\end{equation}
\begin{numcases}{\text{s.t.}}
\Delta_l \sim \mathcal{N} \left(\mu_l,\sigma_l^2\right) & \\
\mu_l = mean\left( \bm{mr}_l , \bm{q}_l \right) & \\
\sigma_l = std\left( \bm{mr}_l , \bm{q}_l \right) & \\
l \in \left\{l' |  ms_{l'} \in \mathcal{S}_{ij,\tau} \right\}  & 
\end{numcases}

@@

\begin{equation}
\max_{\forall \bm{k}}\left( \delta_{\bm{k}}, 
R\left( F\left( mr_{\bm{k}} \right) \right), \abs{\mathcal{L}_{\bm{k},\tau} }
\right)
\end{equation}

\begin{numcases}{\text{s.t.}}
q_{\alpha,ij} \le C_{k_{\alpha},\tau} & $\alpha\in\mathcal{A}_{ij}$\\
R_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{ij,\tau}, P(mr) = \alpha \right\} & $\alpha\in\mathcal{A}_{ij}$\\
\mathcal{R}_{ij,\tau} = \bigcup_{\alpha\in\mathcal{A}_{ij}}\mathcal{R}_{\alpha,\tau} & \\
\bm{k} = \left[k_1,\dots ,k_\alpha,\dots,k_{\abs{\mathcal{A}_{ij}}} \right] & \\
k_\alpha \in \left\{ k | mr_k \in \mathcal{R}_{\alpha,\tau} \right\} &$\alpha\in\mathcal{A}_{ij}$
\end{numcases}
For each required resource type $\alpha$

@@

\begin{gather}
\max_{m\in\{l^*,\bm{k}^*\}} \left( \Delta_m, 
Rank_m, \mathcal{L}_m \right) \\ 
\text{s.t.}\notag
\end{gather}
\begin{numcases}{}
q_{\alpha,ij} \le C_{k_{\alpha},\tau} & \footnotesize$\alpha\in\mathcal{A}_{ij}$\\
R_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{ij,\tau}, P(mr) = \alpha \right\} & \footnotesize$\alpha\in\mathcal{A}_{ij}$\\
\mathcal{R}_{ij,\tau} = \bigcup_{\alpha\in\mathcal{A}_{ij}}\mathcal{R}_{\alpha,\tau} & \\
\bm{k} = \left[k_1,\dots ,k_\alpha,\dots,k_{\abs{\mathcal{A}_{ij}}} \right]& \\
k_\alpha \in \left\{ k | mr_k \in \mathcal{R}_{\alpha,\tau} \right\} &\footnotesize$\alpha\in\mathcal{A}_{ij}$ \\
\bm{k}^* = \arg\left(\max_{\forall \bm{k}}\left( \delta_{\bm{k}}, 
R\left( F\left( mr_{\bm{k}} \right) \right), \abs{\mathcal{L}_{\bm{k},\tau} }
\right)\right) & \\
Rank_{\bm{k}^*} = \min_{k\in\bm{k}^*} \left\{ R\left( F\left( mr_k \right) \right) \right\} & \\
\mathcal{L}_{\bm{k}^*} = \max_{k\in\bm{k}^*}\left\{ \abs{\mathcal{L}_{k,\tau}} \right\} & \\
\Delta_{\bm{k}^*} \sim \mathcal{N} \left(\mu_{\bm{k}^*},\sigma_{\bm{k}^*}^2\right) & \\
\mu_{\bm{k}^*} = mean\left( \bm{mr}_{\bm{k}^*} , \bm{q}_{\bm{k}^*} \right) & \\
\sigma_{\bm{k}^*} = std\left( \bm{mr}_{\bm{k}^*} , \bm{q}_{\bm{k}^*} \right) & \\
\bm{mr}_{\bm{k}^*} = \bigcup_{k\in\bm{k}^*}mr_k  &\\
\bm{q}_{\bm{k}^*}  =\bigcup_{\alpha\in\mathcal{A}_{ij}}q_{\alpha,ij} & \\
\Delta_l \sim \mathcal{N} \left(\mu_l,\sigma_l^2\right) & \\
\mu_l = mean\left( \bm{mr}_l , \bm{q}_l \right) & \\
\sigma_l = std\left( \bm{mr}_l , \bm{q}_l \right) & \\
l \in \left\{l' |  ms_{l'} \in \mathcal{S}_{ij,\tau} \right\}  & \\
l^* = \arg\left( \max_{\forall l}\left(\Delta_{l}, R\left(F\left(ms_{l}\right)\right), \abs{\mathcal{L}_{l,\tau}}\right)  \right) & \\
Rank_{l^*} = R\left( F\left( ms_{l^*} \right) \right) & \\
\mathcal{L}_{l^*} = \abs{\mathcal{L}_{l^*,\tau}} & \\
m \in \left\{ l^*,\bm{k}^* \right\}
\end{numcases}

\subsubsection{Provider}
\label{subs:Provider}
Provider makes decision for job response with regard to its resources and service, the job here is the generalization of task and service-call. As we mentioned in the master plan, provider publish service-call according to the frequent accomplished tasks. Without loss of generalization, we suppose at time $\tau$, demander will make these decisions:

@@

Capacity will not return back to $mr_k$ until the corresponding service $ms_l$ was repealed. Decision making of provider $p_b$ likes the one of demander's, but the final decision $\bm{mr}_l$ and $\bm{q}_l$ don't have to meet $\abs{\bm{mr}_l} = \abs{\mathcal{A}_{ij}}$, because different resource with the same type can gather together to bundle into one service, the only condition in need is that
\begin{numcases}{}
\sum_{k\in\mathcal{R}_{\alpha,\tau}} q_{\alpha,k} = q_{\alpha,l} & $\forall\alpha\in\mathcal{A}_l$\\
R_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{l,\tau}, P(mr) = \alpha \right\} & $\forall\alpha\in\mathcal{A}_l$
\end{numcases}
\resume{asparaenum}
\item Response for the task need $t_{ij}$($\tau\ge r_i$) with service $ms_l$.
\end{asparaenum}
Service is a combination contract among the participated resources and it's made oriented to the certain task, so the only condition for $ms_l$ to response $t_{ij}$ is:
\begin{numcases}{}
q_{\alpha,ij} = q_{\alpha,l} & $\forall\alpha\in\mathcal{B}_l$\\
\mathcal{A}_{ij} = \mathcal{B}_l
\end{numcases}

@@

\subsection{Operation mode} % (fold)
\label{sub:operation_mode}
The chief decision making about operation mode for provider is the job schedule method outsource mode, as we mentioned in the master plan, provider makes these decision to arrange the job for a better performance in the process procedure. Because of the event driven assumptions, we again suppose that both a new task was assigned to service or resource and a job was finished at time $\tau$, provider will make decision in the following conditions:
\begin{asparaenum}
\item Assign new task $t_{ij}$ in $mr_k$.
\suspend{asparaenum}

With the select decision of $t_{ij}$ to assign on $mr_k$ at $\tau$, the first thing for the provider of $mr_k$ is to set the predecessor set:
\begin{equation}
	\mathcal{P}_{ij} := \mathcal{P}_{ij}\cup \left\{ sc| sc\in\mathcal{L}_{k,\tau},sc \text{ is service-call} \right\} \cup \mathcal{G}_{k,\tau}
\end{equation}
Then, the provider will add $t_{ij}$ to queue or process buffer according to:
\begin{numcases}{}
\mathcal{G}_{k,\tau} := \mathcal{G}_{k,\tau} \cup \{t_{ij}\} & if $\abs{\mathcal{L}_{k,\tau}}=0$ and $A_{k,\tau}\ge q_{\alpha,ij}$ \\
\mathcal{L}_{k,\tau} := \mathcal{L}_{k,\tau} \cup \{t_{ij}\} & otherwise
\end{numcases}

\resume{asparaenum}
\item Assign new service-call $sc_l$ in $mr_k$.
\suspend{asparaenum}

With the select decision of $sc_l$ to assign on $mr_k$ at $\tau$, the first thing for the provider of $mr_k$ is to set the predecessor set:
\begin{equation}
	\mathcal{P}_l := \mathcal{P}_l\cup \mathcal{L}_{k,\tau} \cup \mathcal{G}_{k,\tau}
\end{equation}
Then, the provider will add $sc_l$ to queue or process buffer according to:
\begin{numcases}{}
\mathcal{G}_{k,\tau} := \mathcal{G}_{k,\tau} \cup \{sc_l\} & if $\abs{\mathcal{L}_{k,\tau}\cup\mathcal{G}_{k,\tau}}=0$ \\
\mathcal{L}_{k,\tau} := \mathcal{L}_{k,\tau} \cup \{t_{ij}\} & otherwise
\end{numcases}

\resume{asparaenum}
\item Schedule the tasks in $\mathcal{L}_{k,\tau}$.
\suspend{asparaenum}

The assignment of new service-call will not driven these decision making event because of the resource capacity consuming feature, so it's necessary to suspend service-call in inactive status until all the job before it in $\mathcal{L}_{k,\tau}$ are finished, at the meantime, all the job come after service-call should be stay in inactive status until the service-call is finished, as shown in \autoref{fig:simplejoblist}, service-call likes partition plate in $\mathcal{L}_{k,\tau}$.  
\begin{figure}[htbp]
	\centering
	\resizebox{.8\textwidth}{!}{\input{figures/service-call}}
	\caption{Simple illustration for one $\mathcal{L}_{k,\tau}$}
	\label{fig:simplejoblist}
\end{figure}
Therefore, the we just need to schedule the tasks before the first service-call in $\mathcal{L}_{k,\tau}$ when one of the active job in $\mathcal{G}_{k,\tau}$ was finished at $\tau_0$, we denote the set of schedule task at this time as $\mathcal{L}^{(s)}_{k,\tau_0}$

A schedule is given by a vector of ideal finish times $\bm{f}^{(s)} = \left[f_1^{(s)}, f_2^{(s)},\dots,f^{s}_n\right],n=\abs{\mathcal{L}^{(s)}_{k,\tau_0}}$. Since the task in $\mathcal{L}^{(s)}_{k,\tau_0}$ and $\mathcal{G}_{k,\tau_0}$ may come from different orders, we here use the single uniform subscript $j$ to distinguish these tasks and their related variables, type subscript $\alpha$ can be ignored for all the job assigned here matches the resource type, so the schedule model is:

\begin{equation}
\min_{\forall\bm{f}^{(s)}}\left( \max_{j\in L^{(s)}}\left\{ f_j^{(s)} - r_j - p_j \right\} \right)
\end{equation}
\begin{numcases}{\text{s.t.}}
L^{(s)} = \left\{j| t_{j}\in \mathcal{L}^{(s)}_{k,\tau_0}\right\} & \\
f^{(s)}_h \le f_j^{(s)} - p_j & $h\in\mathcal{P}_j$,$j\in L^{(s)}$\\
G^{(s)} = \left\{j' | t_{j'}\in \mathcal{G}_{k,\tau_0}\right\} & \\
f^{(s)}_j =  \tau_0 + re_j & $j\in G^{(s)}$ \\
\sum_{j\in\left\{  j' |t_{j'} \in\mathcal{G}_{k,\tau}\right\}} q_j \le A_{k,\tau}& $\tau \ge \tau_0$ \\
% \bm{f}^{(s)} = \left[f_1^{(s)}, f_2^{(s)},\dots,f^{s}_{\abs{\mathcal{L}^{(s)}_{k,\tau_0}}}\right] & \\
f^{(s)}_j \ge \tau_0 + p_j & $j\in L^{(s)}$
\end{numcases}
\resume{asparaenum}
\item Schedule the task in $\mathcal{L}_{l,\tau}$
\suspend{asparaenum}

\resume{asparaenum}
\item Outsource the task in $\mathcal{L}_{l,
\tau}$ and $\mathcal{P}_{l,\tau}$
\end{asparaenum}
